%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Jiewen}{Hai}
\address{Room 8/F Front Portion, No. 425S, Queen's Road West , Western District, Hong Kong}
\mobile{(+852) 69964094}

\email{hjwissac@gmail.com}
\github{Sredeption}

\position{Computer Science} % Your expertise/fields

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{Company Recruitment Team}{JPMorgan Chase} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Personal Statement} % The title of the letter

\letteropening{Dear Recruiting Manager,} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

I am writing to apply for the Summer Analyst at JPMorgan Chase, since I am fully qualified for this job.

Zhejiang University offer me with solid undergraduate education in Computer Science. I have strong foundation
in computer system, software engineering, computer graphics and artificial intelligence. And now I am studying
in University of Hong Kong, where I could further my study in distributed system.

Rich development experience endows me with expertise to design solid system. Object oriented programming 
allow me to apply various design pattern in the project, such as factory, observer and command. All my
java-based web application adopt Spring framework. Inversion of Control helps me decouple modules with
each other. SpringMVC used to be my favorite framework to implement RESTful service rapidly. Nowadays,
I try to utilized NIO framework Netty to implement high performance service over both HTTP and TCP
protocol. Besides, all the requests parsed by Netty are processed by RxJava without any blocking.

Distributed system interests me because it's very useful in production. Every commercial system has to handle fault 
tolerance, consistency and trade off them with performance. Also, there are lots of problem unsolved in 
this field, which means I might make contribution. Now, I am learning it by building a raft-based sharded key-value 
store with high availability and high consistency.

JPMorgan Chase is a reputable financial firm which has keen need on processing large volume of data in high availability. 
I could certainly employ my skills and enhance myself.

\begin{cvletter}

%------------------------------------------------



%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}